---
title: "Writing Documents in RMarkdown"
author: "Neal Marquez"
date: "February 21, 2019"
header-includes:
   - \usepackage{dcolumn}
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: no
fig_width: 4.8
fig_height: 3.6 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    fig.width=4.8, fig.height=3.6, echo=FALSE, warning=FALSE, message=FALSE)
```

# R Markdown

R Markdown is a great way to not only inspect your data but also share your research with others who may not be as technically inclined as yourself. It should be seen as a tool that streamlines the process between analysis and dissemination of your work.

```{r table1}

library(tidyverse)
library(knitr)
library(stargazer)

kable(summary(cars), caption = "My table", booktabs=T)
```

```{r table2}
kable(summary(iris[,1:4]), caption = "My table 2", booktabs=T)
```

```{r table3, results='asis'}
# system('git clone https://github.com/cran/stargazer')
# system('cd stargazer && git pull -r https://github.com/jiewpeng/stargazer_bookdown')
# devtools::install_git('stargazer')
##  2 OLS models
linear.1 <- lm(rating ~ complaints + privileges + learning + raises + critical,data=attitude)
linear.2 <- lm(rating ~ complaints + privileges + learning, data=attitude)
## create an indicator dependent variable, and run a probit model
attitude$high.rating <- (attitude$rating > 70)
probit.model <- glm(high.rating ~ learning + critical + advance, data=attitude,family = binomial(link = "probit"))
stargazer(linear.1, 
          linear.2, 
          probit.model, title="Results", align=TRUE, header = F, 
          type = ifelse(knitr::is_latex_output(),"latex","html"),
          label = knitr::opts_current$get("label"))
```
# Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE, fig.cap="\\label{fig:pressure} Exponential Growth"}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


\begin{equation}
Y = \text{exp}(\beta_0 + \beta_1 X)
(\#eq:expo)
\end{equation}

See equation \@ref(eq:expo) and Figure \@ref(fig:external) and table \@ref(tab:table3)

```{r external, fig.cap="\\label{fig:external} Exponential Growth", out.width="20%", out.height="20%"}
f_ <- tempfile(fileext = ".jpeg")
download.file(
    "https://pbs.twimg.com/profile_images/426136263960190976/AuCq7Rhs_400x400.jpeg", f_)
include_graphics(f_)
```
